---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rejection Sampling Function for 1-Dimensional Samples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

**Background** 
Rejection sampling is one method of collecting a random sample from along a single dimension.  Rejection sampling works as follows: 
* First, two uniform samples are produced, paired, and plotted.  In this case, pairs of samples were produced and plotted 1000 times.  Each of the x values in this case are 

However, users of this package might be interested in sampling from non-uniform distributions.  In that case, the x values will not be equally likely.  


```{r}
n <- 10
x <- runif(n,0,1)
y <- runif(n,0,1)
points <- cbind(x,y)
names(points) <- c("x", "y")
dark_sample <- data.frame()
light_sample <- data.frame()

pdf <- function(x) {exp(-x)}

for(i in 1:n) {
  dark <- points[i,2] < pdf(points[i,1])
  if(dark) dark_sample <- rbind(dark_sample, points[i,]) else light_sample <- rbind(light_sample, points[i,])
}

print(dark_sample)

library(ggplot2)

?ggplot

ggplot(data = dark_sample, aes(x = "x", y = "y")) +
  geom_point(aes(color = "black"))

geom_point(light_sample, aes(x = x, y = y, col = "gray")) + stat_function(fun = pdf)

stat_function(fun = pdf)

fun.1 <- function(x) x^2 + x
stat_function(fun = fun.1)



df1 <- data.frame(x = seq(2, 8, by = 2),
                  y = seq(30, 15, by = -5))
df2 <- data.frame(x = seq(2, 8, by = 2),
                  y = seq(12, 24, by = 4))

ggplot(df1, aes(x, log(y))) + 
   geom_line() +
   geom_line(data = df2, color = "red")

```


**Example #1: Standard Normal Distribution**
```{r}
pdf <- function(x) {dnorm(x,0,1)}
sample <- THEFUNCTION1D(pdf, n = 100000, lower_bound = -5, upper_bound = 5, C = 0.4)
print(sample)
hist(sample)
```


**Example #2: Uniform distribution(a=-10, b=10)**
```{r}
pdf <- function(x) {dunif(x,-10,10)}
THEFUNCTION1D(pdf, n = 20, lower_bound = -10, upper_bound = 10, C = 0.06)
```

**Example #3: Exponential(lambda = 7)**
```{r}
pdf <- function(x) {dexp(x,7)}
THEFUNCTION1D(pdf, n = 8, lower_bound = 0, upper_bound = 100, C = 50)
```


**Example #4: Gamma(alpha = 12, beta = 0.6)**
```{r}
pdf <- function(x) {dgamma(x, 12, 0.6)}
THEFUNCTION1D(pdf, n = 100, lower_bound = 0, upper_bound = 100, C = 50)
```

**Example #5: Beta(alpha = 6, beta = 8)**
```{r}
pdf <- function(x) {dbeta(x,6,8)}
THEFUNCTION1D(pdf, n = 100, lower_bound = 0, upper_bound = 1, C = 1)
```


